Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Improvments to academic writing style (no more usage of simple, easy, trivial, very, etc.)

    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure composed of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$. It has been extensively studied previously (see~\cite[Fig. 1]{Steudel_2010},~\cite[Fig. 6]{Chaves_2014},~\cite[Fig. 8]{Branciard_2012},~\cite[Fig. 8, App. E]{Henson_2014},~\cite[Fig. 3]{Fritz_2012},~\cite[Fig. 1]{Inflation}, $\ldots$). An overview of some milestone results is provided in \cref{sec:triangle_structure}. Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\cite{Branciard_2012}. Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the Triangle structure.

@@

    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$. Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$. Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then each $n$ should be conditionally independent of all other variables:
    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
    % , except its own descendants when conditioned over $\Pa[\graph]{n}$. This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e. for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
    % \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \Cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is trivially easy to verify whether or not $\prob[\nodes]$ is compatible with $\graph$ by simply computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two naive approaches worth mentioning here. The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$. The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$. Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions. Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}. The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}. An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed. In most realistic scenarios, the nature of the latent variables is completely unspecified. More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions. We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}. In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.

@@

    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing a simple relabeling: $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A}_r, \p{B}_r, \p A_l, \p B_l$. As an example, the famous CHSH inequality~\cite{CHSH_Original} (\cref{eq:CHSH_ineq_orig}) constrains the correlation between the right-bits of $A$ and $B$,

@@

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}. Unfortunately, none of these inequalities could be violated. These early results suggest, although do not prove, that quantum non-classicality does not exist in the Triangle structure for \textit{two-outcome} measurements. Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than two outcomes in at least one variable. Pursuant to this conjecture, this work expands the search for quantum-accessible incompatibility in Triangle structure by increasing the cardinality of outcomes.

    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly suggests the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution. The Inflation Technique has been shown to completely solve the classical causal inference problem~\cite{Navascues_2017} --- indicating that these undiscovered inequalities can be generated using sufficiently complex inflations. The 37 inequalities in~\cite{Inflation} were derived using the Spiral inflation (\cref{fig:spiral_inflation}) and their failure motivated us to consider larger inflations such as those in \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}.

    These incipient insights were sufficient for focusing the search for new inequalities to $4$-outcomes which are violated by the Fritz distribution. \Cref{sec:found_inequalities} expands on our understanding of non-classicality in the Triangle structure by reporting the discovery of these inequalities which admit quantum-accessible violations. As a by-product, this research supports illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.

@@

    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle structure}.

@@

    \section{Numerical Optimizations \& Noisy Distributions}
    \label{sec:violations_noise}
    Causal compatibility inequalities, including those derived in \cref{sec:found_inequalities}, offer an avenue into studying quantum non-classicality. Ultimately, the motivation for finding these inequalities is binary: the first is to classify differing distributions by their compatibility with a given causal structure, and the second is to measure the degree in which a given distribution is non-classical. This approach has been well-studied in the Bell structure, where extremal non-classical correlations maximally violate Bell inequalities~\cite{PR_1995}. However, inequalities are just a singular example of numerous distinct measures of non-classicality~\cite[Section 5]{Vicente_2014}. Alternatives include measuring the non-local content, robustness to noise, or even the classical simulation cost of a given distribution. For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best. The inequalities derived in this report are likely \textit{not} the best measures of non-classicality simply because they have be curated toward the Fritz distribution. Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations. In this section, two measures are used that make use of these compatibility inequalities: robustness to noise and direct numerical violation.

@@

    \subsection{Noisy Distributions}
    \label{sec:noise}
    % \begin{figure}
    % \begin{center}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
    %         \vspace{-0.2in}
    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
    %         \label{fig:uniform_distribution}
    % \end{center}
    % \end{figure}
    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality. As was mentioned in \cref{sec:fritz_distribution}, this embedding required a very idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$. From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}. It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic. Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$, which is trivially compatible with the Triangle structure. The objective of this section is to quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before the reported inequalities fail to witness incompatibility. The associated quantifier used was an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ where $\s{N}_{\vep}$ denotes an \term{$\vep$-noisy Fritz distribution},
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    As $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. Our tests suggest that $I\tsb{Web}$ is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I\tsb{Web}$; an exhaustive search has not been conducted.

@@

    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e. $V_F \defined \max_{P}\bc{I\br{P}/I\br{P_F}}$. The first inequality in consideration is $I\tsb{Web}$. At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$. Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution. In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e. the same set of possible events. This result is not entirely unexpected. As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure. Consequently, it seems that $I\tsb{Web}$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution very closely.

@@

    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible. Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations. These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.

@@

    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{ai-expressible sets} of $\graph'$.

    % A ai-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
    % \[  \]
    % Application of the inflation lemma to linear inequalities constraining ai-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.

    \subsection{Exemplary Inflations of The Triangle structure}
    \label{sec:exemplary_inflations_of_the_triangle structure}

>>>>

    The Triangle structure (\cref{fig:triangle_structure}) is a causal structure composed of $3$ parties labeled $A, B, C$ arranged in a triangular configuration while pair-wise sharing hidden/latent variables $X, Y, Z$. It has been extensively studied previously (see~\cite[Fig. 1]{Steudel_2010},~\cite[Fig. 6]{Chaves_2014},~\cite[Fig. 8]{Branciard_2012},~\cite[Fig. 8, App. E]{Henson_2014},~\cite[Fig. 3]{Fritz_2012},~\cite[Fig. 4]{Weilenmann_2016},~\cite[Fig. 1]{Inflation}, $\ldots$). An overview of some milestone results is provided in \cref{sec:triangle_structure}. Identifying causal compatibility inequalities for this configuration has been seen as particularly challenging~\cite{Branciard_2012}. Further identifying causal compatibility inequalities of such high resolution that such inequalities can be violated by quantum-accessible distributions has remained out-of-reach for the Triangle structure.

@@

    Now that the notion of a causal structure $\graph$ is defined along with some standard graph-theoretic notation, it is now possible to precisely define the notion of compatibility between $\graph$ and a probability distribution $\prob[\nodes]$ defined over the nodes of $\graph$. Intuitively, the absence of certain causal connections within $\graph$ should limit the set of possible observations that can be made on $\graph$. Specifically, the causal structure $\graph$ hypothesizes that if each variable $n \in \nodes$ is causally influenced by its parents $\Pa[\graph]{n}$, then each $n$ should be conditionally independent of all other variables:
    \[ \prob[\nodes] = \prod_{n \in \nodes} \prob[n \mid \Pa[\graph]{n}] = \prob[n_1 \mid \Pa[\graph]{n_1}] \times \cdots \times \prob[n_k \mid \Pa[\graph]{n_k}] \eq \label{eq:compatibility_as_factorization}\]
    % , except its own descendants when conditioned over $\Pa[\graph]{n}$. This is known as the \term{local Markov property}:\footnote{Here $A \indep B \mid C$ denotes statistical independence between $A$ and $B$ conditional on $C$ where $A,B,C \subseteq \nodes$, i.e. for a given probability distribution $\prob[\nodes]$, $\prob[AB \mid C] = \prob[A \mid C]\prob[B \mid C]$.}
    % \[ n \indep \br{\nodes \setminus \De[\graph]{n}} \mid \Pa[\graph]{n} \quad \forall n \in \nodes \eq \label{eq:local_markov_property} \]
    If a given distribution $\prob[\nodes]$ defined over \textit{all} of the nodes $\nodes$ of $\graph$ satisfies \cref{eq:compatibility_as_factorization}, then $\prob[\nodes]$ is said to be \term{compatible with $\graph$}. The conditional distributions in \cref{eq:compatibility_as_factorization} (i.e. $\{\prob[n \mid \Pa[\graph]{n}] \mid n \in \nodes\}$) are referred to as a set of \term{causal parameters for $\graph$}. If a distribution $\prob[\nodes]$ cannot be factorized according to \cref{eq:compatibility_as_factorization}, $\prob[\nodes]$ is said to be \term{incompatible} with $\graph$. The compatibility of a distribution $\prob[\nodes]$ with a causal structure $\graph$ pursuant to \Cref{eq:compatibility_as_factorization} is equivalent to the requirement that $\prob[\nodes]$ obeys all of the conditional independence constraints implied by the \textit{d-separation relations} between variables/nodes in $\graph$~\cite{Pearl_2009}. When one is specified with a joint distribution $\prob[\nodes]$ defined over all nodes of a causal structure $\graph$, it is possible to completely determine whether or not $\prob[\nodes]$ is compatible with $\graph$ by computing the causal parameters induced by $\prob[\nodes]$ and checking the equality of \cref{eq:compatibility_as_factorization}.

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two naive approaches worth mentioning here. The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$. The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$. Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions. Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}. The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}. An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed. In most realistic scenarios, the nature of the latent variables is completely unspecified. More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions. We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}. In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.

@@

    Provided that $C$ is perfectly correlated with $A_l$ and $B_l$, any Bell inequality for the Bell structure defined over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ can be directly converted to an inequality for the Triangle structure by performing a the following relabeling: $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}} \mapsto \p{A}_r, \p{B}_r, \p A_l, \p B_l$. As an example, the famous CHSH inequality~\cite{CHSH_Original} (\cref{eq:CHSH_ineq_orig}) constrains the correlation between the right-bits of $A$ and $B$,

@@

    As a preliminary search for quantum incompatibility in the Triangle structure, we performed numerical optimizations using bipartite qubit density matrices and $2$-outcome POVM measurements against the compatibility inequalities printed in~\cite{Inflation} as well as the entropic inequalities presented by \citet{Henson_2014}. Unfortunately, none of these inequalities could be violated. Furthermore, none of these inequalities were violated by any 2-outcome coarse-graining of the Fritz distribution. These early results suggest, although do not prove, that quantum non-classicality does not exist in the Triangle structure for \textit{two-outcome} measurements. Therefore, it is conjectured that all quantum non-classical distributions in the Triangle structure must utilize more than two outcomes in at least one variable. Pursuant to this conjecture, this work expands the search for quantum-accessible incompatibility in Triangle structure by increasing the cardinality of outcomes.

    Moreover, the existence of the Fritz distribution (\cref{sec:fritz_distribution}) directly demonstrates that quantum-accessible incompatibility exists in the Triangle structure and indirectly proves the existence of causal compatibility inequalities capable of witnessing the non-classicality of the Fritz distribution. The Inflation Technique has been shown to completely solve the classical causal inference problem~\cite{Navascues_2017} --- indicating that these undiscovered inequalities can be generated using sufficiently complex inflations. The 37 inequalities in~\cite{Inflation} were derived using the Spiral inflation (\cref{fig:spiral_inflation}) and their failure motivated us to consider larger inflations such as those in \cref{fig:wagon_wheel_inflation,fig:the_web_inflation}.

    These incipient insights were sufficient for focusing the search for new inequalities sensitive enough to be violated by the Fritz distribution. \Cref{sec:found_inequalities} reports the discovery of these inequalities which expand on our understanding of non-classicality in the Triangle structure. As a by-product, this research illuminates the advantage in using the Inflation Technique to find inequalities for interesting causal structures in general.

@@

    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    I\tsb{WagonWheel} : \\
    + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
    - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
    - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
    - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
    - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
    - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
    - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
    - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
    - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
    - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
    - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the identically named inflation (\cref{fig:wagon_wheel_inflation}) utilized to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_main_summary,sec:exemplary_inflations_of_the_triangle_structure}.

@@

    \section{Numerical Optimizations \& Noisy Distributions}
    \label{sec:violations_noise}
    Causal compatibility inequalities, including those derived in \cref{sec:found_inequalities}, offer an avenue into studying quantum non-classicality. Ultimately, the motivation for finding these inequalities is binary: the first is to classify differing distributions by their compatibility with a given causal structure, and the second is to measure the degree in which a given distribution is non-classical. This approach has been well-studied in the Bell structure, where extremal non-classical correlations maximally violate Bell inequalities~\cite{PR_1995}. However, inequalities are just a singular example of numerous distinct measures of non-classicality~\cite[Section 5]{Vicente_2014}. Alternatives include measuring the non-local content, robustness to noise, or even the classical simulation cost of a given distribution. For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best. The inequalities derived in this report are likely \textit{not} the best measures of non-classicality because they have be curated toward the Fritz distribution. Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations. In this section, two measures are used that make use of these compatibility inequalities: robustness to noise and direct numerical violation.

@@

    \subsection{Noisy Distributions}
    \label{sec:noise}
    % \begin{figure}
    % \begin{center}
    %         \includegraphics[scale=0.6,trim={0 0 0 0.4in},clip]{../../figures/distributions/uniform_dist_plot.pdf}
    %         \vspace{-0.2in}
    %         \[ \probplotvalue{255, 255, 109} = \f{1}{64} \]
    %         \caption{The completely uniform distribution $\s{U}$ visualized using a $4 \times 4 \times 4$ grid.}
    %         \label{fig:uniform_distribution}
    % \end{center}
    % \end{figure}
    In his original work, \citet{Fritz_2012} was able to find quantum non-classicality in the Triangle structure by embedding Bell non-classicality. As was mentioned in \cref{sec:fritz_distribution}, this embedding required an idealistic condition to hold: perfect correlations between $C$ and $A_l, B_l$. From an experimental point of view, it is impossible to use Fritz's original argument to confirm non-classicality because every observable distribution is subject to \text{noise}. It is possible to minimize noise by developing more accurate measurement channels but perfect correlations are too idealistic. Causal compatibility inequalities not only permit there to be noise within a set of observations, but they also provide a means of quantifying the amount of noise that is allowed before non-classicality breaks down.

    For Triangle structure, we define a completely noisy observation as the uniform probability distribution $\s{U}\br{abc} = \s{U}_{ABC}\br{abc} = \f{1}{64} \quad \forall a,b,c\in \bc{0,1,2,3}$\footnote{The completely noisy observation is compatible with the Triangle structure}. The objective of this section is to quantify how much statistical noise can be added to the Fritz distribution $\prob[\fritz]$ before the reported inequalities fail to witness incompatibility. The associated quantifier used was an affine noise parameter $\vep$ such that $0 \leq \vep \leq 1$ where $\s{N}_{\vep}$ denotes an \term{$\vep$-noisy Fritz distribution},
    \[ \s{N}_{\vep} = \br{1 - \vep} \prob[\fritz] + \vep \s{U} \]
    As $\vep$ varies from $0$ to $1$, more and more noise is added to the Fritz distribution and $\s{N}_{\vep}$ transitions from an incompatible distribution $\s{N}_{0} = \prob[\fritz]$ to a compatible distribution $\s{N}_{1} = \s{U}$. Our tests suggest that $I\tsb{Web}$ is most robust to noise and demonstrates that the Fritz distribution remains incompatible with the Triangle structure up to a noise parameter of $\vep \simeq 0.085$. The associated distribution $\s N_{0.085}$ is plotted in \cref{fig:noisy_fritz}. Of course, there remains the possibility that another inequality will be able to withstand a larger degree of noise than $I\tsb{Web}$; an exhaustive search has not been conducted.

@@

    To quantify the degree in which each inequality $I$ could be further violated, we define a relative violation $V_F$ to be the maximum violation relative to the violation achieved by the Fritz distribution, i.e. $V_F \defined \max_{P}\bc{I\br{P}/I\br{P_F}}$. The first inequality in consideration is $I\tsb{Web}$. At best, numerical optimizations converged to a distribution (\cref{fig:maximum_violation_I_1}) with relative violation $V_F \simeq 1.501$. Almost immediately, it is evident that \cref{fig:maximum_violation_I_1} closely resembles the Fritz distribution. In fact, \cref{fig:maximum_violation_I_1} and \cref{fig:fritz_distribution_visualized} share the exact same \textit{possibilistic structure}, i.e. the same set of possible events. This result is not entirely unexpected. As was mentioned in \cref{sec:found_inequalities}, these inequalities are derived specifically to prove the incompatibility of the Fritz distribution and the Triangle structure. Consequently, it seems that $I\tsb{Web}$ only has the capacity to demonstrate incompatibility for distributions that resemble the Fritz distribution closely.

@@

    The question, as proposed by \ref{r:2}, is: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible. Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes: the first corresponding to $A, B$ correlations and the second corresponding to $A, B$ anti-correlations. These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and is a recommended focus for future research.

@@

    % Not all sets $N' \subseteq \nodes'$ can be written as the disjoint union of injectable sets, but those that \textit{can} are called the \term{as-expressible sets} of $\graph'$.

    % A as-expressible set $N'$ is of primal importance to the Inflation Technique because any distribution over $N'$ will factorize according to its ancestral independence conditions
    % \[  \]
    % Application of the inflation lemma to linear inequalities constraining as-expressible distributions $\prob[N']$ transforms those inequalities into polynomial inequalities over the injectable distributions, allowing one to replace all terms with probability distributions defined over variables in $\nodes$.

    \subsection{Exemplary Inflations of The Triangle structure}
    \label{sec:exemplary_inflations_of_the_triangle_structure}

    \Cref{sec:inflation_technique_main_summary} explains how the Inflation Technique~\cite{Inflation} was used to derive novel causal compatibility inequalities for the Triangle structure by constructing inflations of the Triangle structure satisfying \cref{eq:inflation_defn}. Explicitly, for a given inflation $\graph'$ of the Triangle structure, one constructs a marginal problem (see \cref{sec:marginal_satisfiability}) for the marginal scenario $\mscenario$ composed of the maximal as-expressible sets of $\graph'$, i.e. $\mscenario = \AnSepExpr[\graph]{\graph'}$. This section acts as a reference for the particular inflations of the Triangle structure that are mentioned throughout this manuscript. Contained within this section is a depiction of each of these inflations in \cref{fig:inflations} as well as a their as-expressible sets. An efficient algorithm for computing the injectable and as-expressible sets of an inflation can be found in~\cite{Inflation}.
